### 2024-04-13 paper/header.tex
Added most of the content from the JuliaCon2023 presentation

% **************GENERATED FILE, DO NOT EDIT**************

\title{Survey.jl - An Efficient Framework for Analysing Complex Surveys}

\author[1]{Ayush Patnaik}
\affil[1]{XKDR Forum}

\keywords{Julia, Survey, Statistics, Sampling}

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Ayush Patnaik},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}

### 2024-05-27 paper/header.tex
Update header.tex
Added co-author
Update paper/header.tex
Co-authored-by: Nadia <76887318+nadiaenh@users.noreply.github.com>

@@
 
+\author[2]{Nadia Enhaili}
+\affil[2]{Simon Fraser University}
+
 \keywords{Julia, Survey, Statistics, Sampling}
@@
 pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
-pdfsubject = {JuliaCon 2022 Proceedings},
+pdfsubject = {JuliaCon 2023 Proceedings},
 pdfauthor = {Ayush Patnaik},

### 2024-09-15 paper/header.tex
Change proceedings year

@@
 \author[1]{Ayush Patnaik}
+\author[2]{Nadia Enhaili}
+\author[3]{Siddhant Chaudhary}
+\author[1]{Shikhar Mishra}
+\author[4]{Iulia Dumitru}
 \affil[1]{XKDR Forum}
-
-\author[2]{Nadia Enhaili}
 \affil[2]{Simon Fraser University}
+\affil[3]{Chennai Mathematical Institute}
+\affil[4]{Politehnica University of Bucharest}
 
@@
 pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
-pdfsubject = {JuliaCon 2023 Proceedings},
-pdfauthor = {Ayush Patnaik},
+pdfsubject = {JuliaCon 2024 Proceedings},
+pdfauthor = {Ayush Patnaik, Nadia Enhaili, Siddhant Chaudhary, Shikhar Mishra, Iulia Dumitru},
 pdfkeywords = {Julia, Survey, Statistics, Sampling},

### 2024-09-15 paper/header.tex
Year is 2023

@@
 pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
-pdfsubject = {JuliaCon 2024 Proceedings},
+pdfsubject = {JuliaCon 2023 Proceedings},
 pdfauthor = {Ayush Patnaik, Nadia Enhaili, Siddhant Chaudhary, Shikhar Mishra, Iulia Dumitru},
